Milestone 2: Core results 01

### 2023-03-31 R_codeP01/reports/MS2_report03_truncated.Rmd
sma adjustment of report

### Lasso: 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/l_pca_c_771_RORprolif.RData")
l_pca_c_771_RORprolif <- report02_out(l_pca_c_771_RORprolif)
```

@@

### ElasticNet: 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/en_pca_c_771_RORprolif.RData")
en_pca_c_771_RORprolif <- report02_out(en_pca_c_771_RORprolif)
```

@@

### Ridge: 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_stack_c_771_RORprolif.RData")
r_stack_c_771_RORprolif <- report02_out_ridge(r_stack_c_771_RORprolif)
```

### Ridge: 771 genes -> ROR-proliferation score + interactions between PCs
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_stack_c_interact_771_RORprolif.RData")
r_stack_c_interact_771_RORprolif <- report02_out_ridge(r_stack_c_interact_771_RORprolif)
```

### Lasso: 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/l_stack_c_771_RORprolif.RData")
l_stack_c_771_RORprolif <- report02_out(l_stack_c_771_RORprolif)
```

### Lasso: 771 genes -> ROR-proliferation score + interactions between PCs
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/l_stack_c_interact_771_RORprolif.RData")
l_stack_c_interact_771_RORprolif <- report02_out(l_stack_c_interact_771_RORprolif)
```

### ElasticNet: 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/en_stack_c_771_RORprolif.RData")
en_stack_c_771_RORprolif <- report02_out(en_stack_c_771_RORprolif)
```

### ElasticNet: 771 genes -> ROR-proliferation score + interactions between PCs
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/en_stack_c_interact_771_RORprolif.RData")
en_stack_c_interact_771_RORprolif <- report02_out(en_stack_c_interact_771_RORprolif)
```

>>>>

### Lasso/pca: 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/l_pca_c_771_RORprolif.RData")
l_pca_c_771_RORprolif <- report02_out(l_pca_c_771_RORprolif)
```

@@

### ElasticNet/pca: 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/en_pca_c_771_RORprolif.RData")
en_pca_c_771_RORprolif <- report02_out(en_pca_c_771_RORprolif)
```

@@

### Ridge/stack: 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_stack_c_771_RORprolif.RData")
r_stack_c_771_RORprolif <- report02_out_ridge(r_stack_c_771_RORprolif)
```

### Ridge/stack: 771 genes -> ROR-proliferation score + interactions between base models
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_stack_c_interact_771_RORprolif.RData")
r_stack_c_interact_771_RORprolif <- report02_out_ridge(r_stack_c_interact_771_RORprolif)
```

### Lasso/stack: 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/l_stack_c_771_RORprolif.RData")
l_stack_c_771_RORprolif <- report02_out(l_stack_c_771_RORprolif)
```

### Lasso/stack: 771 genes -> ROR-proliferation score + interactions between base models
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/l_stack_c_interact_771_RORprolif.RData")
l_stack_c_interact_771_RORprolif <- report02_out(l_stack_c_interact_771_RORprolif)
```

### ElasticNet/stack: 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/en_stack_c_771_RORprolif.RData")
en_stack_c_771_RORprolif <- report02_out(en_stack_c_771_RORprolif)
```

### ElasticNet/stack: 771 genes -> ROR-proliferation score + interactions base models
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/en_stack_c_interact_771_RORprolif.RData")
en_stack_c_interact_771_RORprolif <- report02_out(en_stack_c_interact_771_RORprolif)
```
